\documentclass[main=english, 12pt, a4paper, sci, utf8, a-1b, online]{aaltothesis}


\usepackage{amsfonts, amssymb, amsbsy, amsmath, amsthm, enumitem}
\usepackage{mathtools, braket, tikz, csquotes, xcolor, graphicx, hyphenat}

\usepackage[capitalize]{cleveref}
\usepackage[parfill]{parskip}

\hyphenpenalty=10000
\tolerance=1000

\input{include/environments.tex}
\input{include/commands.tex}

%% THESIS INFO
\degreeprogram{Computer Science}
\major{Computer Science}
\code{SCI3028.kand}
\univdegree{BSc}
\thesisauthor{Peik Etzell}
\thesistitle{Motion planning for parallel robots on a grid: An overview}
\place{Espoo}
\date{\today}
\supervisor{University Lecturer  \ Henrik Wallén}
\advisor{Postdoctoral researcher \ Francesco d'Amore}
\uselogo{aaltoRed}{''}

%% THE ENGLISH ABSTRACT:
%% Thesis keywords:
\keywords{minimum, makespan, distance, optimization, discrete, NP-complete, complexity, approximation}

%% The abstract text. This text is included in the metadata of the pdf file as well
%% as the abstract page.
\thesisabstract{
This thesis explores coordinated multi-robot motion planning on a discrete grid.
We first investigate minimum makespan motion planning, proving that its formulation as a decision problem is NP-hard by simplifying a reduction from a previous work by Demaine et al.
We then provide an overview of two current approximation algorithms that efficiently compute schedules with a guaranteed level of robot performance.
We finally extend a previous theorem by Yu and LaValle to hold specifically on the grid, showing that optimizing different cost functions will result in different output schedules.
Although the scope is limited to the discrete case, we acknowledge that more efficient schedules are possible in the continuous domain, but this domain is less well-understood.
Overall, this thesis provides valuable insights into the field of coordinated motion planning on a discrete grid, paving the way for future research in this area.
}

%% Copyright text. Copyright of a work is with the creator/author of the work
%% regardless of whether the copyright mark is explicitly in the work or not.
%% You may, if you wish, publish your work under a Creative Commons license (see
%% creativecommons.org), in which case the license text must be visible in the
%% work. Write here the copyright text you want. It is written into the metadata
%% of the pdf file as well.
%% Syntax:
%% \copyrigthtext{metadata text}{text visible on the page}

\copyrighttext{Copyright \noexpand\copyright\ \number\year\ \ThesisAuthor}
{Copyright \copyright{} \number\year{} \ThesisAuthor}


\begin{document}

%% Create the coverpage
\makecoverpage

\makecopyrightpage

% Skip numbering until introduction
\pagenumbering{gobble}

%% ENGLISH ABSTRACT
%% All the details (name, title, etc.) on the abstract page appear as specified
%% above.
\begin{abstractpage}[english]
    \abstracttext{}
\end{abstractpage}

%% Force new page so that the Swedish abstract starts from a new page
\newpage

%% SWEDISH ABSTRACT.
\thesistitle{Rörelseplanering för parallella robotar i ett rutnät: en översikt}
\supervisor{Universitetslektor \ Henrik Wallén}
\advisor{Postdoktoral forskare \ Francesco d'Amore}
\degreeprogram{Datateknik}
\major{Datateknik}
\keywords{tidsspann, avstånd, optimering, diskret, NP-komplett, komplexitet}
\begin{abstractpage}[swedish]
Denna avhandling undersöker koordinerad rörelseplanering av flera robotar i ett diskret rutnät.
Vi utforskar först problemet av att räkna ut en rörelseplan med minsta möjliga tidsspann, och visar att dess formulering som beslutsproblem är NP-komplett genom en förenklad reduktion av Demaine et al.
Sedan ges en översikt över två approximationsalgoritmer som effektivt kan beräkna rörelseplaner med en garanterad nivå av robotprestanda.
Slutligen utvidgar vi ett tidigare teorem av Yu och LaValle för att gälla specifikt på ett rutnät, vilket visar att optimering av olika kostnadsfunktioner ger olika rörelseplaner som resultat.
Även om avhandlingen har ett begränsat fokus på den diskreta modellen av problemet, erkänner vi att mer effektiva rörelseplaner är möjliga med en kontinuerlig modell, men det området är dock mindre väl förstått.
Avhandlingen ger värdefulla insikter inom koordinerad rörelseplanering på ett rutnät, och banar väg för framtida forskning inom området.
\end{abstractpage}


% %% PREFACE
% %% This section is optional.
% \mysection{Preface}

% \vspace{5cm}
% Espoo, \today

% \vspace{5mm}
% {\hfill Peik Etzell \hspace{1cm}}

\newpage


%% TABLE OF CONTENTS
\thesistableofcontents
\cleardoublepage

% Start numbering from introduction
\pagenumbering{arabic}

% INTRODUCTION
\input{chapters/1-introduction.tex}

% PRELIMINARIES 
\input{chapters/2-preliminaries.tex}

% PROOF THAT THE PROBLEM IS NP-HARD 
\input{chapters/main/3-computational_complexity.tex}

% TWO EFFICIENT ALGORITHMS
\input{chapters/main/4-approximation_algorithms.tex}

% PROOF THAT PAIRWISE OPTIMIZATION IS NOT GENERALLY POSSIBLE
\input{chapters/main/5-simultaneous_opt.tex}

% CONCLUSIONS
\input{chapters/6-conclusions.tex}

\newpage
% Skip numbering references -pages
% \pagenumbering{gobble}

%% REFERENCES
% \renewcommand{\thepage}{}
\thispagestyle{empty}
\bibliographystyle{plain}
\bibliography{manual_refs}
\thispagestyle{empty}
\clearpage


%% ADD POSSIBLE APPENDIX HERE
\thesisappendix

\end{document}
